---
title: "longitudinal plots"
author: "Rachel Lee"
date: "4/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data}

library(tidyverse)

cmpst_all = read_csv(file = "/Users/rachellee/Google Drive/Practicum/Data/cmpst_all.csv") %>%
 janitor::clean_names() %>%
 mutate( visit = forcats::fct_relevel(visit, c("Screen", "Baseline", "Week3", "Week6", "Week9", "Week14", "Week24")))

```


HVLT: 

```{r hvlt}

#data = cmpst_all
#plot, x = visit, y = var of interest, grouped by "patient_id"

ggplot(cmpst_all, aes(visit, hvlt_immed, group = patient_id) ) + geom_point() + geom_line()

ggplot(cmpst_all, aes(visit, hvlt_discrim, group = patient_id) ) + geom_point() + geom_line()

```

Comments: Lots of loss to follow-up. Patient longitudinal analysis difficult. 


Treatment Rationale Scale

```{r trs_total}

ggplot(cmpst_all, aes(visit, trs_total, group = patient_id) ) + geom_point() + geom_line()

```
Comments: Only week 3 and week 14 data available. Logitudinal analysis for each patient impossible. 



PANAS

```{r PANAS}

ggplot(cmpst_all, aes(visit, pos_affect, group = patient_id) ) + geom_point() + geom_line()

ggplot(cmpst_all, aes(visit, neg_affect, group = patient_id) ) + geom_point() + geom_line()

```

Comments: No observable trend in change. "neg_affect" decline with time? 


MADRS: 

```{r MADRS}

ggplot(cmpst_all, aes(visit, madrs_total, group = patient_id) ) + geom_point() + geom_line()

```
Comments: Decline in "madrs_total" with time 


```{r DSSI}

ggplot(cmpst_all, aes(visit, dssi_si, group = patient_id) ) + geom_point() + geom_line()


ggplot(cmpst_all, aes(visit, dssi_ss, group = patient_id) ) + geom_point() + geom_line()


ggplot(cmpst_all, aes(visit, dssi_is, group = patient_id) ) + geom_point() + geom_line()


ggplot(cmpst_all, aes(visit, dssi_net, group = patient_id) ) + geom_point() + geom_line()


```

Comments: No observable trend. Week 9, 14, 24 data analysis could be possible. 




Writing Functions: 

```{r functions}

long_plot <- function(x_arg, y_arg) {
  cmpst_all
  ggplot(cmpst_all, aes (x= x_arg, y = y_arg, group = patient_id)) + geom_point() + geom_line()
}

long_plot(visit, hvlt_immed)

```



