---
title: "PrelimPlots"
author: "Rachel Lee"
date: "4/3/2020"
output: html_document
---
```{r data}
library(tidyverse)


cmpst_all = read_csv(file = "/Users/rachellee/Google Drive/Practicum/Data/cmpst_all.csv") %>%
 janitor::clean_names() %>%
 mutate( visit = forcats::fct_relevel(visit, c("Screen", "Baseline", "Week3", "Week6", "Week9", "Week14", "Week24")))


#names(cmpst_all)


str(cmpst_all)


```

Stroop: The Stroop Color and Word Test (SCWT) is a neuropsychological test extensively used to assess the ability to inhibit cognitive interference that occurs when the processing of a specific stimulus feature impedes the simultaneous processing of a second stimulus attribute, well-known as the Stroop Effect. 

```{r stroop}

#baseline data 

cmpst_all %>%
  select(patient_id, visit, stroop_color, stroop_word, stroop_color_word) %>%
  filter(visit == "Baseline") %>%
  drop_na() %>%
  summarize(
    n(),
    mean_color = mean(stroop_color),
    sd_color = sd(stroop_color), 
    mean_word = mean(stroop_word),
    sd_word = sd(stroop_word),
    mean_colorword = mean(stroop_color_word),
    sd_colorword = sd(stroop_color_word)
  ) %>%
 knitr::kable()
  
```


HVLT: Hopkins Verbal Learning test, assess acquisition and delayed recall, detecting the earliest signs of dementia 

```{r hvlt_immed}

#longitudinal plots
cmpst_hvlt <- select(cmpst_all, patient_id, gender, visit, hvlt_immed, hvlt_discrim) 

cmpst_hvlt %>%
  filter(patient_id == 4000) %>%
  ggplot(aes(x=visit, y = hvlt_immed)) +
  geom_point() 


#calculate the difference
cmpst_hvlt_immed <- cmpst_hvlt %>%
  select(patient_id, gender, visit, hvlt_immed) %>%
  drop_na() %>%
 pivot_wider(
  names_from = "visit",
  values_from = "hvlt_immed",
  ) %>%
  select(-Week24) %>%
  mutate(
    change = Week14 - Baseline
  )

cmpst_hvlt_immed 

```

Comment: Lots of observations are missing Week14. 


```{r hvlt_discrim}



#calculate the difference
cmpst_hvlt_discrim <- cmpst_all %>%
  select(patient_id, gender, visit, hvlt_discrim) %>%
  drop_na() %>%
 pivot_wider(
  names_from = "visit",
  values_from = "hvlt_discrim",
  ) %>%
  select(-Week24) %>%
  mutate(
    change = Week14 - Baseline
  )

cmpst_hvlt_discrim

```

Comment: Lots of observations are missing Week14. 



Treatment Rational Scale

```{r trs}
cmpst_trs <- cmpst_all %>%
  select(patient_id, gender, visit, trs_total) 

#longitudinal plot

cmpst_trs %>%
  filter(patient_id == 4001) %>%
  ggplot(aes(x=visit, y=trs_total)) +
  geom_point()


#calculate the difference

cmpst_trs <- cmpst_all %>%
  select(patient_id, gender, visit, trs_total) %>%
  drop_na() %>%
 pivot_wider(
  names_from = "visit",
  values_from = "trs_total",
  ) %>%
  mutate(
    change = Week14 - Week3
  )

cmpst_trs

```


PANAS: Positive & Negative Affect 
Scores can range from 10-50 for both the Positive and Negative Affect with the lower scores representing lower levels of Positive/Negative Affect and higher scores representing higher levels of Positive/Negative Affect. Participants utilizing PANAS use a 5-point scale in which they determine if a concept applies. 

```{r panas}

cmpst_panas <- cmpst_all %>%
  select(patient_id, gender, visit, pos_affect, neg_affect) 

cmpst_panas_pos <- cmpst_panas %>%
  select(patient_id, gender, visit, pos_affect)

cmpst_panas_neg <- cmpst_panas %>%
  select(patient_id, gender, visit, neg_affect)

#Logitudinal plot

cmpst_panas_pos %>%
  filter(patient_id == 4001) %>%
  ggplot(aes(x=visit, y=pos_affect)) +
  geom_point() 

cmpst_panas_neg %>%
  filter(patient_id == 4001) %>%
  ggplot(aes(x=visit, y=neg_affect)) +
  geom_point()

##calculate the difference of posaffect

cmpst_panas_pos <- cmpst_panas_pos %>%
  drop_na() %>%
 pivot_wider(
  names_from = "visit",
  values_from = "pos_affect",
  ) %>%
  mutate(
    change = Week14 - Baseline
  )
cmpst_panas_pos

##calculate the difference of negaffect

cmpst_panas_neg <- cmpst_panas_neg %>%
  drop_na() %>%
 pivot_wider(
  names_from = "visit",
  values_from = "neg_affect",
  ) %>%
  mutate(
    change = Week14 - Baseline
  )
cmpst_panas_neg


```

Montgomery-Åsberg Depression Rating Scale. 
This test is used by clinicians to assess the severity of depression among patients who have a diagnosis of depression. The MADRS includes 10 items and uses a 0 to 6 severity scale, scored following the interview.  Higher scores indicate increasing depressive symptoms. Ratings can be added to form an overall score (range 0 to 50); no weights are used. Cut-off points include: 0 to 6 – symptom absent, 7 to 19 – mild depression, 30 to 34 – moderate, 35 to 60 – severe depression. 

```{r madrs}
cmpst_madrs <- cmpst_all %>%
  select(patient_id, gender, visit, madrs_total) 

cmpst_madrs

#Logitudinal plot

cmpst_madrs %>%
  filter(patient_id == 4007) %>%
  ggplot(aes(x = visit, y = madrs_total )) +
  geom_point() 


##calculate the difference of negaffect


cmpst_madrs <- cmpst_madrs %>%
   mutate( visit = forcats::fct_relevel(visit, c("Screen", "Baseline", "Week3", "Week6", "Week9", "Week14", "Week24"))) %>%
  drop_na() %>%
 pivot_wider(
  names_from = "visit",
  values_from = "madrs_total",
  ) %>%
  mutate(
    change = Week14 - Baseline
  ) %>%
   janitor::clean_names() %>%
  select(-end_of_treatment) 




cmpst_madrs
```





```{r dssi}

```


```{r whoq}

```

