---
title: "summarystatistics"
author: "Rachel Lee"
date: "4/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r data}

library(tidyverse)

cmpst_all = read_csv(file = "/Users/rachellee/Google Drive/Practicum/Data/cmpst_all.csv") %>%
 janitor::clean_names() %>%
 mutate( visit = forcats::fct_relevel(visit, c("Screen", "Baseline", "Week3", "Week6", "Week9", "Week14", "Week24")))

```

Stroop: The Stroop Color and Word Test (SCWT) is a neuropsychological test extensively used to assess the ability to inhibit cognitive interference that occurs when the processing of a specific stimulus feature impedes the simultaneous processing of a second stimulus attribute, well-known as the Stroop Effect. 

Stroop_Color

```{r StroopColorBL}

cmpst_stroop_color <- cmpst_all %>%
  select(patient_id, visit, stroop_color) %>%
  filter(visit == "Baseline") 


cmpst_stroop_color %>%
  drop_na() %>%
  summarize(
    n(),
    mean_color = mean(stroop_color),
    sd_color = sd(stroop_color), 
    median_color = median(stroop_color),
    iqr_color = IQR(stroop_color)
  ) %>%
 knitr::kable()

#Count missing
cmpst_stroop_color %>%
  select(stroop_color) %>%
  summarise_all(funs(sum(is.na(.))))

#Quantile
quantile(cmpst_stroop_color$stroop_color, na.rm = TRUE)

```


Stroop_Word

```{r StroopWordBL}

cmpst_stroop_word <- cmpst_all %>%
  select(patient_id, visit, stroop_word) %>%
  filter(visit == "Baseline") 


cmpst_stroop_word %>%
  drop_na() %>%
  summarize(
    n(),
    mean_word = mean(stroop_word),
    sd_word = sd(stroop_word), 
    median_word = median(stroop_word),
    iqr_word = IQR(stroop_word)
  ) %>%
 knitr::kable()

#Count missing
cmpst_stroop_word %>%
  select(stroop_word) %>%
  summarise_all(funs(sum(is.na(.))))

#Quantile
quantile(cmpst_stroop_word$stroop_word, na.rm = TRUE)

```


Stroop_Color_Word

```{r StroopColorWordBL}

cmpst_stroop_color_word <- cmpst_all %>%
  select(patient_id, visit, stroop_color_word) %>%
  filter(visit == "Baseline") 

#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_stroop_color_word %>%
  drop_na() %>%
  summarize(
    n(),
    mean_color = mean(stroop_color_word),
    sd_color = sd(stroop_color_word), 
    median_color = median(stroop_color_word),
    iqr_color = IQR(stroop_color_word)
  ) %>%
 knitr::kable()

##Count missing
cmpst_stroop_color_word %>%
  select(stroop_color_word) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_stroop_color_word$stroop_color_word, na.rm = TRUE)

```


HVLT: Hopkins Verbal Learning test, assess acquisition and delayed recall, detecting the earliest signs of dementia. Includes 'hvlt_immed' and 'hvlt_discrim'


i) hvlt_immed at baseline

```{r hvlt_immed_baseline}

#extract hvlt_immed and hvlt_discrim
cmpst_hvlt <- select(cmpst_all, patient_id, gender, visit, hvlt_immed, hvlt_discrim) 

#extract hvlt_immed
cmpst_hvlt_immed <- cmpst_hvlt %>%
  select(patient_id, gender, visit, hvlt_immed) 

#hvlt_immed at baseline
cmpst_hvlt_immed_bl <- cmpst_hvlt_immed %>%
  filter(visit == "Baseline")

#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_hvlt_immed_bl %>%
  drop_na() %>%
  summarize(
    n(),
    mean_color = mean(hvlt_immed),
    sd_color = sd(hvlt_immed), 
    median_color = median(hvlt_immed),
    iqr_color = IQR(hvlt_immed)
  ) %>%
 knitr::kable()

##Count missing
cmpst_hvlt_immed_bl %>%
  select(hvlt_immed) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_hvlt_immed_bl$hvlt_immed, na.rm = TRUE)

```

ii) hvlt_immed at week 14

```{r hvlt_immed_week14}

#extract hvlt_immed at week14
cmpst_hvlt_immed_wk14 <- cmpst_hvlt_immed %>%
  filter(visit == "Week14")


#Week14 Summary Statistics


##N, mean, sd, median, IQR
cmpst_hvlt_immed_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean_color = mean(hvlt_immed),
    sd_color = sd(hvlt_immed), 
    median_color = median(hvlt_immed),
    iqr_color = IQR(hvlt_immed)
  ) %>%
 knitr::kable()

##Count missing
cmpst_hvlt_immed_wk14 %>%
  select(hvlt_immed) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_hvlt_immed_wk14$hvlt_immed, na.rm = TRUE)
```

Note: only 10 non-missing observations at week 14 


iii) hvlt_discrim at baseline

```{r hvlt_discrim_baseline}

#extract hvlt_discrim
cmpst_hvlt_discrim <- cmpst_hvlt %>%
  select(patient_id, gender, visit, hvlt_discrim) 

#hvlt_discrim at baseline
cmpst_hvlt_discrim_bl <- cmpst_hvlt_discrim %>%
  filter(visit == "Baseline")

#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_hvlt_discrim_bl %>%
  drop_na() %>%
  summarize(
    n(),
    mean_color = mean(hvlt_discrim),
    sd_color = sd(hvlt_discrim), 
    median_color = median(hvlt_discrim),
    iqr_color = IQR(hvlt_discrim)
  ) %>%
 knitr::kable()

##Count missing
cmpst_hvlt_discrim_bl %>%
  select(hvlt_discrim) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_hvlt_discrim_bl$hvlt_discrim, na.rm = TRUE)

```

iv) hvlt_discrim at week 14

```{r}


#hvlt_discrim at week 14
cmpst_hvlt_discrim_wk14 <- cmpst_hvlt_discrim %>%
  filter(visit == "Week14")

#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_hvlt_discrim_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean_color = mean(hvlt_discrim),
    sd_color = sd(hvlt_discrim), 
    median_color = median(hvlt_discrim),
    iqr_color = IQR(hvlt_discrim)
  ) %>%
 knitr::kable()

##Count missing
cmpst_hvlt_discrim_wk14 %>%
  select(hvlt_discrim) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_hvlt_discrim_wk14$hvlt_discrim, na.rm = TRUE)

```

Note: only 10 non-missing observations at week 14 
























