---
title: "summarystatistics"
author: "Rachel Lee"
date: "4/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r data}

library(tidyverse)

cmpst_all = read_csv(file = "/Users/rachellee/Google Drive/Practicum/Data/cmpst_all.csv") %>%
 janitor::clean_names() %>%
 mutate( visit = forcats::fct_relevel(visit, c("Screen", "Baseline", "Week3", "Week6", "Week9", "Week14", "Week24")))

```

Stroop: The Stroop Color and Word Test (SCWT) is a neuropsychological test extensively used to assess the ability to inhibit cognitive interference that occurs when the processing of a specific stimulus feature impedes the simultaneous processing of a second stimulus attribute, well-known as the Stroop Effect. 

Stroop_Color

```{r StroopColorBL}

cmpst_stroop_color <- cmpst_all %>%
  select(patient_id, visit, stroop_color) %>%
  filter(visit == "Baseline") 


cmpst_stroop_color %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(stroop_color),
    sd = sd(stroop_color), 
    median = median(stroop_color),
    IQR = IQR(stroop_color)
  ) %>%
 knitr::kable()

#Count missing
cmpst_stroop_color %>%
  select(stroop_color) %>%
  summarise_all(funs(sum(is.na(.))))

#Quantile
quantile(cmpst_stroop_color$stroop_color, na.rm = TRUE)

```


Stroop_Word

```{r StroopWordBL}

cmpst_stroop_word <- cmpst_all %>%
  select(patient_id, visit, stroop_word) %>%
  filter(visit == "Baseline") 


cmpst_stroop_word %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(stroop_word),
    sd = sd(stroop_word), 
    median = median(stroop_word),
    IQR = IQR(stroop_word)
  ) %>%
 knitr::kable()

#Count missing
cmpst_stroop_word %>%
  select(stroop_word) %>%
  summarise_all(funs(sum(is.na(.))))

#Quantile
quantile(cmpst_stroop_word$stroop_word, na.rm = TRUE)

```


Stroop_Color_Word

```{r StroopColorWordBL}

cmpst_stroop_color_word <- cmpst_all %>%
  select(patient_id, visit, stroop_color_word) %>%
  filter(visit == "Baseline") 

#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_stroop_color_word %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(stroop_color_word),
    sd = sd(stroop_color_word), 
    median = median(stroop_color_word),
    IQR = IQR(stroop_color_word)
  ) %>%
 knitr::kable()

##Count missing
cmpst_stroop_color_word %>%
  select(stroop_color_word) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_stroop_color_word$stroop_color_word, na.rm = TRUE)

```


HVLT: Hopkins Verbal Learning test, assess acquisition and delayed recall, detecting the earliest signs of dementia. Includes 'hvlt_immed' and 'hvlt_discrim'


i) hvlt_immed at baseline

```{r hvlt_immed_baseline}

#extract hvlt_immed and hvlt_discrim
cmpst_hvlt <- select(cmpst_all, patient_id, gender, visit, hvlt_immed, hvlt_discrim) 

#extract hvlt_immed
cmpst_hvlt_immed <- cmpst_hvlt %>%
  select(patient_id, gender, visit, hvlt_immed) 

#hvlt_immed at baseline
cmpst_hvlt_immed_bl <- cmpst_hvlt_immed %>%
  filter(visit == "Baseline")

#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_hvlt_immed_bl %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(hvlt_immed),
    sd = sd(hvlt_immed), 
    median = median(hvlt_immed),
    IQR = IQR(hvlt_immed)
  ) %>%
 knitr::kable()

##Count missing
cmpst_hvlt_immed_bl %>%
  select(hvlt_immed) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_hvlt_immed_bl$hvlt_immed, na.rm = TRUE)

```

ii) hvlt_immed at week 14

```{r hvlt_immed_week14}

#extract hvlt_immed at week14
cmpst_hvlt_immed_wk14 <- cmpst_hvlt_immed %>%
  filter(visit == "Week14")


#Week14 Summary Statistics


##N, mean, sd, median, IQR
cmpst_hvlt_immed_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(hvlt_immed),
    sd = sd(hvlt_immed), 
    median = median(hvlt_immed),
    iqr = IQR(hvlt_immed)
  ) %>%
 knitr::kable()

##Count missing
cmpst_hvlt_immed_wk14 %>%
  select(hvlt_immed) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_hvlt_immed_wk14$hvlt_immed, na.rm = TRUE)
```

Note: only 10 non-missing observations at week 14 


iii) hvlt_discrim at baseline

```{r hvlt_discrim_baseline}

#extract hvlt_discrim
cmpst_hvlt_discrim <- cmpst_hvlt %>%
  select(patient_id, gender, visit, hvlt_discrim) 

#hvlt_discrim at baseline
cmpst_hvlt_discrim_bl <- cmpst_hvlt_discrim %>%
  filter(visit == "Baseline")

#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_hvlt_discrim_bl %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(hvlt_discrim),
    sd = sd(hvlt_discrim), 
    median = median(hvlt_discrim),
    IQR = IQR(hvlt_discrim)
  ) %>%
 knitr::kable()

##Count missing
cmpst_hvlt_discrim_bl %>%
  select(hvlt_discrim) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_hvlt_discrim_bl$hvlt_discrim, na.rm = TRUE)

```

iv) hvlt_discrim at week 14

```{r hvlt_discrim_wk14}


#hvlt_discrim at week 14
cmpst_hvlt_discrim_wk14 <- cmpst_hvlt_discrim %>%
  filter(visit == "Week14")

#Week14 Summary Statistics

##N, mean, sd, median, IQR
cmpst_hvlt_discrim_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(hvlt_discrim),
    sd = sd(hvlt_discrim), 
    median = median(hvlt_discrim),
    IQR = IQR(hvlt_discrim)
  ) %>%
 knitr::kable()

##Count missing
cmpst_hvlt_discrim_wk14 %>%
  select(hvlt_discrim) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_hvlt_discrim_wk14$hvlt_discrim, na.rm = TRUE)

```

Note: only 10 non-missing observations at week 14 


Treatment Rational Scale

Since TRS does not have baseline data, we will treat week 3 as baseline.

```{r trs_total_wk3}

#extract trs_total

cmpst_trs_total <- cmpst_all %>%
  select(patient_id, gender, visit, trs_total) 


#trs_total at week3
cmpst_trs_total_wk3 <- cmpst_trs_total %>%
  filter(visit == "Week3")



#Week3 Summary Statistics

##N, mean, sd, median, IQR
cmpst_trs_total_wk3 %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(trs_total),
    sd = sd(trs_total), 
    median = median(trs_total),
    IQR = IQR(trs_total)
  ) %>%
 knitr::kable()

##Count missing
cmpst_trs_total_wk3 %>%
  select(trs_total) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_trs_total_wk3$trs_total, na.rm = TRUE)


```


```{r trs_total_wk14}

#trs_total at week14
cmpst_trs_total_wk14 <- cmpst_trs_total %>%
  filter(visit == "Week14")



#Week3 Summary Statistics

##N, mean, sd, median, IQR
cmpst_trs_total_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean= mean(trs_total),
    sd = sd(trs_total), 
    median = median(trs_total),
    IQR = IQR(trs_total)
  ) %>%
 knitr::kable()

##Count missing
cmpst_trs_total_wk14 %>%
  select(trs_total) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_trs_total_wk14$trs_total, na.rm = TRUE)

```


PANAS: Positive & Negative Affect 
Scores can range from 10-50 for both the Positive and Negative Affect with the lower scores representing lower levels of Positive/Negative Affect and higher scores representing higher levels of Positive/Negative Affect. Participants utilizing PANAS use a 5-point scale in which they determine if a concept applies. 


Positive Affect

```{r panas_positive_bl}


#extract pos_affect 

cmpst_pos_affect <- cmpst_all %>%
  select(patient_id, gender, visit, pos_affect) 


#pos_affect at baseline
cmpst_pos_affect_bl <- cmpst_pos_affect %>%
  filter(visit == "Baseline")



#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_pos_affect_bl %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(pos_affect),
    sd = sd(pos_affect), 
    median = median(pos_affect),
    IQR = IQR(pos_affect)
  ) %>%
 knitr::kable()

##Count missing
cmpst_pos_affect_bl %>%
  select(pos_affect) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_pos_affect_bl$pos_affect, na.rm = TRUE)


```


```{r panas_positive_wk14}

#pos_affect at week14
cmpst_pos_affect_wk14 <- cmpst_pos_affect %>%
  filter(visit == "Week14")

#Week14 Summary Statistics

##N, mean, sd, median, IQR
cmpst_pos_affect_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(pos_affect),
    sd = sd(pos_affect), 
    median = median(pos_affect),
    IQR = IQR(pos_affect)
  ) %>%
 knitr::kable()

##Count missing
cmpst_pos_affect_wk14 %>%
  select(pos_affect) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_pos_affect_wk14$pos_affect, na.rm = TRUE)

```



Negative Affect

```{r panas_negative_bl}

#extract neg_affect 

cmpst_neg_affect <- cmpst_all %>%
  select(patient_id, gender, visit, neg_affect) 

#pos_affect at baseline
cmpst_neg_affect_bl <- cmpst_neg_affect %>%
  filter(visit == "Baseline")



#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_neg_affect_bl %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(neg_affect),
    sd = sd(neg_affect), 
    median = median(neg_affect),
    IQR = IQR(neg_affect)
  ) %>%
 knitr::kable()

##Count missing
cmpst_neg_affect_bl %>%
  select(neg_affect) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_neg_affect_bl$neg_affect, na.rm = TRUE)


```


```{r panas_negative_wk14}

#neg_affect at week14
cmpst_neg_affect_wk14 <- cmpst_neg_affect %>%
  filter(visit == "Week14")

#Week14 Summary Statistics

##N, mean, sd, median, IQR
cmpst_neg_affect_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(neg_affect),
    sd = sd(neg_affect), 
    median = median(neg_affect),
    IQR = IQR(neg_affect)
  ) %>%
 knitr::kable()

##Count missing
cmpst_neg_affect_wk14 %>%
  select(neg_affect) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_neg_affect_wk14$neg_affect, na.rm = TRUE)

```


Montgomery-Åsberg Depression Rating Scale (MADRS) 
This test is used by clinicians to assess the severity of depression among patients who have a diagnosis of depression. The MADRS includes 10 items and uses a 0 to 6 severity scale, scored following the interview.  Higher scores indicate increasing depressive symptoms. Ratings can be added to form an overall score (range 0 to 50); no weights are used. Cut-off points include: 0 to 6 – symptom absent, 7 to 19 – mild depression, 30 to 34 – moderate, 35 to 60 – severe depression. 


MADRS at Baseline

```{r madrs_bl}

#exttract madrs_total

cmpst_madrs <- cmpst_all %>%
  select(patient_id, gender, visit, madrs_total) 


#madrs_total at baseline
cmpst_madrs_bl <- cmpst_madrs %>%
  filter(visit == "Baseline")


#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_madrs_bl %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(madrs_total),
    sd = sd(madrs_total), 
    median = median(madrs_total),
    IQR = IQR(madrs_total)
  ) %>%
 knitr::kable()

##Count missing
cmpst_madrs_bl %>%
  select(madrs_total) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_madrs_bl$madrs_total, na.rm = TRUE)


```

MADRS at Week 14

```{r madrs_wk14}

#madrs_total at week14
cmpst_madrs_wk14 <- cmpst_madrs %>%
  filter(visit == "Week14")


#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_madrs_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(madrs_total),
    sd = sd(madrs_total), 
    median = median(madrs_total),
    IQR = IQR(madrs_total)
  ) %>%
 knitr::kable()

##Count missing
cmpst_madrs_wk14 %>%
  select(madrs_total) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_madrs_wk14$madrs_total, na.rm = TRUE)

```


DSSI

Duke Social Support Index (DSSI) - Used to measure social support of the elderly. The 35-item DSSI measures multiple dimensions of social support of the elderly. The 23-item and 11-item versions have been used for the chronically ill and frail elderly.

subscales: 
i) DSSI-SI: social interaction 
ii) DSSI-SS: subjective support
iii) DSSI-IS: instrumental support  13-24
iv) DSSI-NET: social networking. 1st question


i-1) dssi_si at baseline

```{r dssi_si_bl}

#exttract dssi_si

cmpst_dssi_si <- cmpst_all %>%
  select(patient_id, gender, visit, dssi_si) 


#dssi_si at baseline
cmpst_dssi_si_bl <- cmpst_dssi_si %>%
  filter(visit == "Baseline")


#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_dssi_si_bl %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(dssi_si),
    sd = sd(dssi_si), 
    median = median(dssi_si),
    IQR = IQR(dssi_si)
  ) %>%
 knitr::kable()

##Count missing
cmpst_dssi_si_bl %>%
  select(dssi_si) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_dssi_si_bl$dssi_si, na.rm = TRUE)


```

i-2) dssi_si at week 14

```{r dssi_si_wk14}

#dssi_si at week14
cmpst_dssi_si_wk14 <- cmpst_dssi_si %>%
  filter(visit == "Week14")


#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_dssi_si_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(dssi_si),
    sd = sd(dssi_si), 
    median = median(dssi_si),
    IQR = IQR(dssi_si)
  ) %>%
 knitr::kable()

##Count missing
cmpst_dssi_si_wk14 %>%
  select(dssi_si) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_dssi_si_wk14$dssi_si, na.rm = TRUE)

```

ii-1) dssi_ss at baseline

```{r}

#exttract dssi_ss

cmpst_dssi_ss <- cmpst_all %>%
  select(patient_id, gender, visit, dssi_ss) 


#dssi_si at baseline
cmpst_dssi_ss_bl <- cmpst_dssi_ss %>%
  filter(visit == "Baseline")


#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_dssi_ss_bl %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(dssi_ss),
    sd = sd(dssi_ss), 
    median = median(dssi_ss),
    IQR = IQR(dssi_ss)
  ) %>%
 knitr::kable()

##Count missing
cmpst_dssi_ss_bl %>%
  select(dssi_ss) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_dssi_ss_bl$dssi_ss, na.rm = TRUE)

```


ii-2) dssi_ss at week 14

```{r}

#dssi_si at week14
cmpst_dssi_ss_wk14 <- cmpst_dssi_ss %>%
  filter(visit == "Week14")


#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_dssi_ss_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(dssi_ss),
    sd = sd(dssi_ss), 
    median = median(dssi_ss),
    IQR = IQR(dssi_ss)
  ) %>%
 knitr::kable()

##Count missing
cmpst_dssi_ss_wk14 %>%
  select(dssi_ss) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_dssi_ss_wk14$dssi_ss, na.rm = TRUE)


```


iii-1) dssi_is at baseline

```{r}

#exttract dssi_is

cmpst_dssi_is <- cmpst_all %>%
  select(patient_id, gender, visit, dssi_is) 


#dssi_si at baseline
cmpst_dssi_is_bl <- cmpst_dssi_is %>%
  filter(visit == "Baseline")


#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_dssi_is_bl %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(dssi_is),
    sd = sd(dssi_is), 
    median = median(dssi_is),
    IQR = IQR(dssi_is)
  ) %>%
 knitr::kable()

##Count missing
cmpst_dssi_is_bl %>%
  select(dssi_is) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_dssi_is_bl$dssi_is, na.rm = TRUE)

```



iii-2) dssi_is at week 14

```{r}

#dssi_si at week14
cmpst_dssi_is_wk14 <- cmpst_dssi_is %>%
  filter(visit == "Week14")


#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_dssi_is_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(dssi_is),
    sd = sd(dssi_is), 
    median = median(dssi_is),
    IQR = IQR(dssi_is)
  ) %>%
 knitr::kable()

##Count missing
cmpst_dssi_is_wk14 %>%
  select(dssi_is) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_dssi_is_wk14$dssi_is, na.rm = TRUE)

```


iv-1) dssi_net at baseline

```{r}

#exttract dssi_net

cmpst_dssi_net <- cmpst_all %>%
  select(patient_id, gender, visit, dssi_net) 


#dssi_net at baseline
cmpst_dssi_net_bl <- cmpst_dssi_net %>%
  filter(visit == "Baseline")


#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_dssi_net_bl %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(dssi_net),
    sd = sd(dssi_net), 
    median = median(dssi_net),
    IQR = IQR(dssi_net)
  ) %>%
 knitr::kable()

##Count missing
cmpst_dssi_net_bl %>%
  select(dssi_net) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_dssi_net_bl$dssi_net, na.rm = TRUE)
```

iv-2) dssi_net at week 14 

```{r}

#dssi_net at week14
cmpst_dssi_net_wk14 <- cmpst_dssi_net %>%
  filter(visit == "Week14")


#Baseline Summary Statistics

##N, mean, sd, median, IQR
cmpst_dssi_net_wk14 %>%
  drop_na() %>%
  summarize(
    n(),
    mean = mean(dssi_net),
    sd = sd(dssi_net), 
    median = median(dssi_net),
    IQR = IQR(dssi_net)
  ) %>%
 knitr::kable()

##Count missing
cmpst_dssi_net_wk14 %>%
  select(dssi_net) %>%
  summarise_all(funs(sum(is.na(.))))

##Quantile
quantile(cmpst_dssi_net_wk14$dssi_net, na.rm = TRUE)
```

